Draft2

### 2022-04-25 population_data.Rmd
issues i ran into when loading file
population data

>>>>

high_pop_countries <- world_pop %>% 
  filter(Year > 1999 & Country.Name %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia')) %>% 
  group_by(Year)

high_pop_countries

low_pop_countries <- world_pop %>% 
  filter(Year > 1999 & Country.Name %in% c('United States', 'Brazil', 'Ethiopia', 'Russia', 'China', 'Australia'))%>% 
  group_by(Year)

low_pop_countries
